---
title: "Air Quality Analysis"
author: "Group 4"
date: "8/4/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

For our assignment, we have selected the "NewYork Air Quality" dataset from https://www.kaggle.com/mfaisalqureshi/newyork-air-quality. This data set has daily air quality measurements from May to September (5 months). The variables in our data set are Ozone, Solar.R, Wind, Temp, Month, and Day. The total number of rows in the dataset is 153.

## Load libraries & import the data
```{r message=FALSE}
library(tidyverse)
Air_Quality<-read.csv(file="airquality.csv")
```

```{r}
str(Air_Quality) #Print the structure
names(Air_Quality) #List the variables
head(Air_Quality, 15) #Print the top 15 rows
```
## User-Defined Function
```{r}
square_of_solar<-function(){
  Air_Quality2<-Air_Quality
  (Air_Quality2$Solar.R)^2
}

square_of_solar()
```

## Filter rows
```{r}
Air_Quality<-filter(Air_Quality, Air_Quality$Wind<10) 
```

\newpage
## Independent Variables: Ozone, Solar.R, Wind, Temp 
## Dependent Variable: Day
## Unused Variable: X
```{r}
Air_Quality <- cbind(Air_Quality$Ozone,
                     Air_Quality$Solar.R, Air_Quality$Wind,
                     Air_Quality$Temp)
Air_Quality = as.data.frame(Air_Quality)
```

## Remove missing values & duplicate rows
```{r results='hide'}
Air_Quality<-na.omit(Air_Quality)
Air_Quality %>% distinct()
```

```{r}
head(Air_Quality, 15)
```

## Rename columns
```{r}
Air_Quality<-rename(Air_Quality, Ozone=V1, Solar_Rad=V2, Wind=V3, Temperature=V4)
```

## Reorder rows in descending order
```{r results='hide'}
Air_Quality %>% arrange(desc(Air_Quality$Ozone)) 
```

## Add new variables
```{r}
Air_Quality$Double_Wind = (Air_Quality$Wind)*2
Air_Quality$Half_Ozone = (Air_Quality$Ozone)/2
head(Air_Quality, 8)
```

## Create a training set using random number generator engine
```{r}
set.seed(1234)
Air_Quality %>% sample_frac(0.80, replace = FALSE) 
```

## Calculate descriptive statistics
```{r}
summary(Air_Quality)
mean(Air_Quality$Ozone)
median(Air_Quality$Ozone)
range(Air_Quality$Ozone)
```

## User-defined mode function
```{r}
user_mode<-function(x){
  modeVal<-unique(x)
  
  #Match returns a vector of the positions of the first 
  #matches of its arguments
  modeVal[which.max(tabulate(match(x, modeVal)))]
}

user_mode(Air_Quality$Ozone)
```

\newpage
## Bar Plot 
```{r}
#Tell geom_bar that y-values will be provided
ggplot(data=Air_Quality, aes(x=Ozone, y=Temperature)) +
  geom_bar(stat="identity", fill="red") +
  labs(y="Temperature")
```

\newpage
## Scatter Plot 
```{r}
#Turn off confidence intervals
ggplot(data=Air_Quality, aes(x=Ozone, y=Temperature)) +
  geom_point(color="red") + labs(y="Temperature") +
  geom_smooth(method='lm', se=FALSE)
```

## Calculate Pearson correlation
```{r}
cor(Air_Quality$Ozone, Air_Quality$Temperature, method="pearson")
```

## Conclusion
Based on our analysis, there is a correlation between
Ozone & Temperature. From the bar plot it can be seen that the temperature reaches its maximum around 25 for ozone. The scatter plot shows an exponential relationship between temperature & ozone.

Github Link: https://github.com/SkySpartan/BUS-4064-Assignment-1.git